Memory-aware Adaptive Scheduling of Scientific Workflows on Heterogeneous Architectures\\

### 2025-03-11 main.tex
temp

    \title{Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
    % \thanks{Identify applicable funding agency here. If none, delete this.}
    }

@@

Overall, there are a variety of memory models, but, to the best of our knowledge, the only study on a multiprocessor
platform that is fully heterogeneous, with individual memories, \new{is our own previous work~\cite{DBLP:conf/icpp/KulaginaMB24}.}
\new{Yet, in that paper we only propose} a partitioning-based mapping of the workflow, without processor reuse.
\new{Since a processor is idle after a workflow partition has finished its execution 
in~\cite{DBLP:conf/icpp/KulaginaMB24},
there is no need for communication buffers to store data
that should be \new{exchanged} between processors when tasks are ready to execute.}

@@

De Olivera~\etal~\cite{de2012provenance} propose a tri-criteria (makespan, reliability, cost) \new{cost model and an adaptive
 scheduling algorithm for clouds (scheduling virtual machines).
The greedy algorithm based on this cost model  works in 4 steps, choosing the best resources type to execute the virtual
machine on, producing new cloud activities, setting up the granularity factor, and finally adapting the amount of resources
to fit the budget.}
The authors test four scenarios -- one preferring each criterion in the cost model and a balanced one.
The authors use workflows with less than ten tasks, but repeat them so that the execution has up to 200 tasks.
%They do not report the runtime of the scheduling algorithm, only the speedup and cost saving it produces.
%   The authors use provenance data to make scheduling decisions.

Daniels \etal~\cite{daniels1995robust} formalize the concept of robust scheduling with variable processing times
on a single machine.
The changes in task running times are not due to changing machine properties, but are rather task-related
and thus unrelated to each other.
The authors search for an optimal schedule
%    formulate a decision space of all permutations of $n$ jobs, and the optimal schedule 
in relation to a performance measure. % $\phi$.
Then they proceed to formulate the Absolute Deviation Robust Scheduling Problem \new{with} a set of linear constraints.

@@

Thus, the scheduler receives deviation values and makes decision based on them.
This leads to several types of possible issues:
%
\begin{itemize}
\item 
  A processor is blocked by another task. If the scheduler underestimated the execution time of a task,
  it will block another one from starting.
\item 
  A predecessor has not finished yet.
  The scheduler may request a task to start on its processor, while
  some of the predecessors of the task have in fact not yet completed their execution -- 
  the task is therefore not yet ready.
%        A similar situation, but a task could start on its processor, but one or more of its parents a
%        are not ready yet.
\item 
  Not enough memory. If the scheduler underestimated the amount of memory a task requires, this task might not be able to execute on a chosen processor.
\item 
  A task took less time than expected. We only consider this case if a task took more than 10\% less
  time than expected. In this case, we want to exploit the newly acquired free time by possibly starting other tasks earlier.
\end{itemize}

\new{We call this execution mode execution \textit{with recomputation}.
Alternatively, the runtime system can execute \textit{without recomputation}.
It then follows the original schedule without sending the deviation values to the scheduler.

In this case, the runtime system waits for a blocked processor to become available if another task scheduled to it takes longer than expected.
If the predecessor task takes longer to execute, the runtime system leaves the processor of the current task
temporarily idle.
If any tasks take less time then expected, the runtime system ignores the opportunity to start other tasks earlier.
Finally, if there is not enough memory, the schedule is declared invalid and the execution stops.

The comparison to the makespan of the execution without recomputation shows how much improvement the exploration of dynamic
changes brings.
Moreover, the number of schedules that manage to stay valid despite the changes is an indicator of their robustness and the quality of the scheduler.
}

>>>>

    \title{Memory-aware Adaptive Scheduling of Scientific Workflows on Heterogeneous Architectures\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
    % \thanks{Identify applicable funding agency here. If none, delete this.}
    }

@@

Overall, there are a variety of memory models, but, to the best of our knowledge, the only study on a multiprocessor
platform that is fully heterogeneous, with individual memories, \new{is our own previous work~\cite{DBLP:conf/icpp/KulaginaMB24}.}
\new{Yet, in that paper, we only propose} a partitioning-based mapping of the workflow, without processor reuse.
\new{Since a processor is idle after a workflow partition has finished its execution 
in~\cite{DBLP:conf/icpp/KulaginaMB24},
there is no need for communication buffers to store data
that should be \new{exchanged} between processors when tasks are ready to execute.}

@@

De Olivera~\etal~\cite{de2012provenance} propose a tri-criteria (makespan, reliability, cost) \new{cost model and an adaptive
 scheduling algorithm for clouds (scheduling virtual machines).
The greedy algorithm based on this cost model  works in four steps, choosing the best resource types to execute the virtual
machine on, producing new cloud activities, setting up the granularity factor, and finally adapting the amount of resources
to fit the budget.}
The authors test four scenarios -- one preferring each criterion in the cost model and a balanced one.
The authors use workflows with less than ten tasks, but repeat them so that the execution has up to 200 tasks.
%They do not report the runtime of the scheduling algorithm, only the speedup and cost saving it produces.
%   The authors use provenance data to make scheduling decisions.

Daniels \etal~\cite{daniels1995robust} formalize the concept of robust scheduling with variable processing times
on a single machine.
The changes in task running times are not due to changing machine properties, but are rather task-related
and thus unrelated to each other.
The authors search for an optimal schedule
%    formulate a decision space of all permutations of $n$ jobs, and the optimal schedule 
in relation to a performance measure. % $\phi$.
Then, they proceed to formulate the Absolute Deviation Robust Scheduling Problem \new{with} a set of linear constraints.

@@

Thus, the scheduler receives deviation values and makes decision based on them\new{, hence
leading to an execution mode  \textit{with recomputation}.}
This leads to several types of possible issues:
%
\begin{itemize}
\item 
  A processor is blocked by another task. If the scheduler underestimated the execution time of a task,
  it will block another one from starting.
\item 
  A predecessor has not finished yet.
  The scheduler may request a task to start on its processor, while
  some of the predecessors of the task have in fact not yet completed their execution -- 
  the task is therefore not yet ready.
%        A similar situation, but a task could start on its processor, but one or more of its parents a
%        are not ready yet.
\item 
  Not enough memory. If the scheduler underestimated the amount of memory a task requires, this task might not be able to execute on a chosen processor.
\item 
  A task took less time than expected. We only consider this case if a task took more than 10\% less
  time than expected. In this case, we want to exploit the newly acquired free time by possibly starting other tasks earlier.
\end{itemize}

\new{Alternatively, the runtime system can execute \textit{without recomputation}.
It then follows the original schedule without sending the deviation values to the scheduler.

In this case, the runtime system waits for a blocked processor to become available if another task scheduled to it takes longer than expected.
If the predecessor task takes longer to execute, the runtime system leaves the processor of the current task
temporarily idle.
If any task takes less time than expected, the runtime system ignores the opportunity to start other tasks earlier.
Finally, if there is not enough memory, the schedule is declared invalid and the execution stops.

The comparison to the makespan of the execution without recomputation shows how much improvement the exploration of dynamic
changes brings.
Moreover, the number of schedules that manage to stay valid despite the changes is an indicator of their robustness and of the quality of the scheduler.}
